Cosmic web correlations with the shape, spin and peculiar velocties of dark matter halos

### 2013-06-07 paper/main.tex
3 new paragraphs

\title[Vweb \& Tweb]{Halo alignments with large scale tidal and
  velocity fields} 
\author[S. Contreras et al.]{
\parbox[t]{\textwidth}{\raggedright 
  Sergio Contreras$^{1}$ 
  Jaime E. Forero-Romero$^{1}$ 
  Nelson Padilla$^{1}$ 
}
\vspace*{6pt}\\
$^{1}$Uni A
$^{2}$Uni B
}
\maketitle

@@

... In this paper we use groups found with a FOF halo finder.

\section{The cosmic web algorithms}
\label{sec:algorithms}

\subsection{The Tidal Web}

\subsection{The Velocity Web}

@@

... In this paper we compute the cosmic web on grids of two different
resolutions $256^3$ and $512^3$.

@@

>>>>

\title[Vweb \& Tweb]{Cosmic web correlations with the shape, spin and
  peculiar velocties of dark matter halos}  
\author[S. Contreras et al.]{
\parbox[t]{\textwidth}{\raggedright 
  Sergio Contreras$^{1}$ 
  Jaime E. Forero-Romero$^{1}$ 
  Nelson Padilla$^{1}$ 
}
\vspace*{6pt}\\
$^{1}$Uni A
$^{2}$Uni B
}
\maketitle

@@

In this paper we use groups found with a FOF halo finder.

\section{The cosmic web algorithms}
\label{sec:algorithms}
We use two algorithms to define the cosmic web on cosmological N-body
simulations. Both are based on the same algorithmic principle, which
is determining locally a symmetric tensor which can be diagonalized to yield
three real eigenvalues $\lambda_1>\lambda_2>\lambda_3$ and their
corresponding eigenvectors ${\bf e}_{1}$, ${\bf e}_2$ and ${\bf
  e}_3$. This allows for a local classification into one of the
following four categories: void, sheet, filament and peak depending
whether the number of eigenvalues larger than a given threshold
$\lambda_{th}$ is $3$, $2$, $1$ or $0$, respectively.

We use two different symmetric tensors. The first is the shear tensor,
defined as the hessian of the gravitational potential, normalized in
such a way as to be dimensionless:

\begin{equation}
T_{\alpha\beta} = \frac{\partial^2\phi}{\partial
  r_{\alpha}\partial r_{\beta}}, 
\end{equation}
where $\phi$ is the gravitational potential rescaled by a factor $4\pi
G\bar{\rho}=3/2\Omega_m H_{0}^2$ in such a way that the Poission
equation can be written as:

\begin{equation}
\nabla^{2}\phi  = \delta, 
\end{equation}

where $\delta$ is the matter overdensity, $\bar{\rho}$ is the average
matter density, $H_{0}$ is the Hubble constant at present time and
$\Omega_m$ is the matter density parameter.

The second tensor is the velocity shear:

\begin{equation}
\Sigma_{\alpha\beta} = -\frac{1}{2H_{0}}\left(\frac{\partial
  v_{\alpha}}{\partial r_{\beta}}+ \frac{\partial v_{\beta}}{\partial
  r_{\alpha}}\right) 
\end{equation}

@@

In this paper we compute the cosmic web on grids of two different
resolutions $256^3$ and $512^3$...

@@

\subsection{Mass dependency and other conditions for stronger alignment}

We wish to understand what other selection criteria on halo
properties can produce a stronger local alignment for the shape, spin
and peculiar velocities. We split the halo population into low and
high mass halos imposing a cut at $M_{\rm halo}=10^{11}$\hMsun. This
allows us to have robust statistics on the high mass end. We have also
computed these results for a cut at $M_{\rm halo}=10^{12}$\hMsun and
checked that the results we report below are not affected by this
change.

For each mass interval we perform cuts in the following properties:
spin, concentration, triaxiallity, circularity  and density. We
measure the web alignments in two sets, each one including the $30\%$
of halos in the lower/higher end of the corresponding property.
